Simulation Comparison

### 2021-04-20 output_scripts/Slide_Plots.Rmd

sim_data %>%
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + 
  geom_boxplot(aes(fill = Method), alpha = 0.7) +
  scale_fill_manual(values = plot_cols) +
  labs(y = "Rank Correlation") + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") #+ ggtitle("(b)")
```

@@

load(paste(data_path,cohort_names[current_cohort],
           "/agg_rank_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

no_method <- 4
plot_latent_df <- data.frame(Methods=rep(1:no_method,each=1000*mice_number),
                             Mice=rep(rep(1:mice_number,each=1000),no_method),
                             force=rep(0,1000*mice_number*no_method))
## agg
plot_latent_df$force[(1:(1000*mice_number))] <- as.vector(sim_agg_rank$x[1001:2000,])

## M1
plot_latent_df$force[(1:(1000*mice_number))+1000*mice_number] <- as.vector(sim_cohort_hp$f)

## M2
plot_latent_df$force[(1:(1000*mice_number))+2000*mice_number] <- as.vector(sim_cohort_dchp$f)

## M3
plot_latent_df$force[(1:(1000*mice_number))+3000*mice_number] <- as.vector(sim_cohort_mmhp$f)

plot_latent_df$Mice <- factor(plot_latent_df$Mice,
                              levels = expert_rank_10[[current_cohort]])
plot_latent_df$Method <- factor(plot_latent_df$Method,
                                labels = c("AggRanking","C-HP","C-DCHP","C-MMHP"))

# png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
plot_cols <- col_df %>% filter(method %in% c("AggRank", "C-HP",
                                "C-DCHP", "C-MMHP")) %>%
  pull(cols)

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols) +
  # ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
#dev.off()

@@

```{r fig-6b-overall-rank-correlation, include=TRUE, eval=TRUE}
load("../output/weighted_rank_data.RData")
#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = plot_cols) + 
        # ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2

>>>>

plot_cols_slide <- col_df %>%
  filter(method %in% levels(sim_data$name)) %>%
  filter(method != "AggRank") %>%
  pull(cols)

sim_data %>%
  filter(name != "AggRank") %>%
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + 
  geom_boxplot(aes(fill = Method), alpha = 0.7) +
  scale_fill_manual(values = plot_cols_slide) +
  labs(y = "Rank Correlation") + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") #+ ggtitle("(b)")
```

@@

# load(paste(data_path,cohort_names[current_cohort],
#            "/agg_rank_stan_result_",cohort_names[current_cohort],
#            ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

no_method <- 3
plot_latent_df <- data.frame(Methods = rep(1:no_method,
                                         each=1000*mice_number),
                             Mice = rep(rep(1:mice_number,each=1000),
                                      no_method),
                             force = rep(0,1000*mice_number*no_method))
# ## agg
# plot_latent_df$force[(1:(1000*mice_number))] <- as.vector(sim_agg_rank$x[1001:2000,])

## M1
plot_latent_df$force[(1:(1000*mice_number))] <-
  as.vector(sim_cohort_hp$f)

## M2
plot_latent_df$force[(1:(1000*mice_number)) + 
                       1000*mice_number] <- as.vector(sim_cohort_dchp$f)

## M3
plot_latent_df$force[(1:(1000*mice_number)) + 
                       2000*mice_number] <- as.vector(sim_cohort_mmhp$f)

plot_latent_df$Mice <- factor(plot_latent_df$Mice,
                              levels = expert_rank_10[[current_cohort]])
plot_latent_df$Method <- factor(plot_latent_df$Method,
                                labels = c("C-HP","C-DCHP","C-MMHP"))

# png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
plot_cols_slide <- col_df %>%
  filter(method %in% c( "C-HP","C-DCHP", "C-MMHP")) %>%
  pull(cols)

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_slide) +
  # ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
#dev.off()

@@

```{r fig-6b-overall-rank-correlation, include=TRUE, eval=TRUE}
load("../output/weighted_rank_data.RData")
#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))

cols_here <- col_df %>% 
  filter(method %in% c("AggRank","C-HP","C-DCHP","C-MMHP")) %>%
  pull(cols)

p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = cols_here) + 
        # ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2

### 2021-04-20 output_scripts/cmmhp_comparison/sim_comparison.Rmd

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_0 = 0.08,
                   sim_lambda_1 = 0.16,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

## Iteration on 50 simulations
for(s in c(1:n_sim)){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

>>>>

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_1 = 0.2,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.05, 0.02, 0.03, 0.08, 0.01),
                   zeta_var = c(0.075, 0.1, 0.05, 0.01, 0.02),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
                         length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1)))
Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1))) 
PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1))) 
PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1))) 
KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1)))
KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
current_sims <- 1:n_sim
# 7,31,34,43,47,49
## Iteration on 50 simulations
# 8,11,19,27,32,42,43,46
for(s in 47:n_sim){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))
